% Calum Gilchrist - Curriculum Vitae
%
% Copyright (C) 2004-2012 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,a4paper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{graphicx}

% Fonts
%\usepackage[T1]{fontenc}
%\usepackage{nimbus}

% Set your name here
\def\name{Calum Gilchrist}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  right=1.0in,
  top=1.0in,
  bottom=1.0in
}

% Customize page headers
\pagestyle{myheadings}
%\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\ttfamily\mdseries\Large}
%\subsectionfont{\ttfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
    \renewcommand{\labelitemi}{$\bullet$}
  }
}{
  \end{list}
}

\begin{document}

% Optionally add Cover Letter
%\include{coverLetter}

% Reset length from cover letter
\setlength{\parskip}{0em}

% Place name at left
%{\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.495\textwidth}
  8 Namayo Avenue, \\
  Laurieston, Falkirk, \\
  Stirlingshire, FK2 9LX
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Mobile: +447869078051 \\
  Email: \href{mailto:me@calumgilchrist.co.uk}{me@calumgilchrist.co.uk} \\
  Homepage: \href{http://calumgilchrist.co.uk/}{http://CalumGilchrist.co.uk}
\end{minipage}

\section*{Education}

\begin{itemize}
    \item BSc Computer Science with Honours of the First Class at Heriot Watt University, Edinburgh, 2014.

    \begin{itemize}
        \item \textbf{Dissertation} \emph{The Effect of using Alternate Name Generation in Geographic Information Systems}. Analysed a variety of techniques to better aid the precision of a spoken word navigation system in identifying named entities in the Open Street Map database.
        \item Two courses of note:
            \begin{itemize}
                \item \textbf{Distributed and Parallel Technologies} \\
                    Exposure to a variety of different parallel programming approaches. Mainly through languages and libraries such as OpenCL and Haskell.
                \item \textbf{Software Engineering} \\
                    A 6 month group project to deliver a tournament organisation application. Implemented using Ruby on Rails.
            \end{itemize}
        \item Received three Certificates of Merit. 
    \end{itemize}

    \item \textbf{Advanced Highers}: Physics [B], Mathematics [B]
    \item \textbf{Highers}: Computer Science [A], Technological Studies [A], Chemistry [A], English [B]
\end{itemize}

\section*{Employment}

\begin{itemize}
    \item \textbf{DevOps Engineer} at \emph{Cloudreach Limited}, May 2013 - Present

    Mixed role dealing with customers for Google Apps and \emph{Amazon Web Service} (\textbf{AWS}) platforms. Troubleshooting and configuration of both environments for a wide variety of customers.
    Experience gained while working at Cloudreach:
    \begin{itemize}
      \item Troubleshooting various AWS products including EC2, VPC and RDS.
      \item Configuration and troubleshooting experience for a variety of Linux and Windows
        applications and servers.
      \item Maintenance and troubleshooting of highly available applications using various AWS and third party technologies.
      \item Programming with Ruby and Google Apps Script for in-house applications such as the travel application form.
      \item Development and deployment of monitoring applications using Chef and Splunk.
      \item Integrated Cloudwatch Metrics with Splunk using CloudFormation, Ruby ERB Templates, SQS and a Ruby client.
    \end{itemize}
\end{itemize}

\section*{Skills Profile}

% Should highlight 5 main topics
%   * Ruby on Rails
%   * Sys admin
%   * Web Programming
%   * Team Work and Management
%   * Communication Skills
\begin{itemize}
    \item Helped develop a prototype Ruby on Rails application for \href{http://www.ScranClan.com}{ScranClan.com}, a startup created during Startup Weekend, Glasgow 2013.
    \item Developed a HTML5 web game in CoffeeScript for a 48 hour game
        competition.
    \item Won first place as part of a team in the Fourth Glasgow Future City Hackathon for a pothole detection and analysis application for use by Glasgow City Council.
    \item Won ``Most Implemented Hack'' at Cyclehack 2014 for a handlebar mounted navigation system using an Arduino.
    \item Have designed, developed and hosted several iterations of personal websites and projects on varying servers and hosting platforms.
    \item Used vanilla JS for UX and to interface with a Symphony backed chat client for the Web Applications course at University.
    \item Worked as an events photographer for the Hippodrome Monster Movie Day, The JRs Charity Concert and for Grangemouth Rugby Football Club.
\end{itemize}

\section*{Technical Skills}

% Relevant technical expertise
%   Applications, databases, PLs, OSs, Projects, Published Work
% Work based evidence

\begin{itemize}
    \item Have used Arch Linux, Debian, Redhat Enterprise Linux and their derivatives for both professional and personal use
    \item Earned the AWS Technical Professional Accreditation, which outlines the basics of the AWS services.
    \item Modified and written compilers and interpreters in a Programming Languages module at University.
    \item Some experience with Unit Testing, primarily with RSpec in RoR.
    \item Application development with Java, Ruby and Python programming languages.
    \item Used the git \emph{version control system} in personal and professional projects
    \item Developed a crowd sourcing application for alternative names for use in dissertation project using Sinatra and MongoDB.
    \item Used Bash and Python scripts for server management and task automation
    \item Familiar with Vagrant for use in creating development environments as part of work at Cloudreach
    \item Manage personal machines using Salt Stack to facilitate configuration management
\end{itemize}

\section*{Additional Information}

\begin{itemize}
    \item Attend monthly meetings at Edinburgh Tech Meetup as well as other Edinburgh based meetups
    \item Presented a talk on alternatives to Bitcoin at the Falkirk
        Linux User Group, April 2014.
    \item Developed and photographed all the headshots used in the Graeme High
        School 2010 Year Book.
    \item Assisted in setting up and running live video for a Battle of
        the Bands.
\end{itemize}

% \section*{Miscellaneous}

% Footer
\medskip
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}
\end{document}
